NanoMaLy

### 2015-11-19 paper/pldi16-submission/evaluation.tex
one more take on the graphs

\paragraph{Trace Explosion}
Though the average complexity of our generated traces is low in terms of
jumps, there are some extreme outliers. We cannot reasonably expect a
novice user to explore a trace containing 50+ terms and draw a
conclusion about which pieces contributed to the bug in their
program. Enhancing our visualization to slice out program paths relevant
to specific values, \eg in the style of~ \cite{perera_functional_2012},
would likely help alleviate this issue. This would allow users to
highlight a confusing value and ask: ``Where did this come from?''

>>>>

\paragraph{Trace Explosion}
Though the average complexity of our generated traces is low in terms of
jumps, there are some extreme outliers. We cannot reasonably expect a
novice user to explore a trace containing 50+ terms and draw a
conclusion about which pieces contributed to the bug in their
program. Enhancing our visualization to slice out program paths relevant
to specific values, \eg in the style of~\cite{perera_functional_2012},
would likely help alleviate this issue, allowing users to
highlight a confusing value and ask: ``Where did this come from?''
